---
title: "How to take on Netflix"
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: 
Ref1: Some Institution, Cape Town, South Africa
Email1: nfkatzke\@gmail.com
Author2: John Smith
Ref2: Some other Institution, Cape Town, South Africa
Email2: John\@gmail.com
CommonAffiliation_12: yes
Author3: John Doe
Email3: Joe\@gmail.com
CorrespAuthor_1: yes
keywords: Multivariate GARCH \sep Kalman Filter \sep Copula
JELCodes: L250 \sep L100
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes

---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(huxtable)
```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->



```{r}
#read in the data
netflix<-read.csv("/Users/ryanyoung/Desktop/Data Science/22575480/data/data/netflix/titles.csv")
```

This bar chart shows the movies/series in the Netflix catalog by release year. As one can see Netflix has a lot of recent movies/series, but far fewer older movies/series in it catalog. Therefore, a competitor could gain market share by offering a wider range of movies/series especially for earlier years. However, maybe people prefer newer movies, this is examined in the second chart.

```{r}
#movie release by year
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 4/code/movies_per_year.R")
plot_movies_released(netflix)
```

This chart shows the average movie/series ratings per year from 2000 on wards using two different movies rating sites. Average movie/film ratings score has decreased since 2000, suggesting that users are less satisfied with some of the newer releases. Netflix's competitors should be aware of this. 

```{r}
#average scores after 2000
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 4/code/line_chart_score.R")
plot_average_scores(netflix)
```


What Netflix has got right is a decent spread of movies/series across different age restrictions as the table belong illustrates. 
```{r}
#table showing age rating 
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 4/code/movie_table_age.R")
movie_counts <- get_movie_counts_by_age(netflix)
movie_counts
```

