---
title: "New York Times Covid Report"
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: "Ryan Young"

Email1: "22575480\\@sun.ac.za"
Author2: John Smith
Ref2: Some other Institution, Cape Town, South Africa
Email2: John\@gmail.com
CommonAffiliation_12: yes
Author3: John Doe
Email3: Joe\@gmail.com
CorrespAuthor_1: yes
keywords: Multivariate GARCH \sep Kalman Filter \sep Copula
JELCodes: L250 \sep L100
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes

---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->




```{r}
#read in data 
covid_data<-read.csv("/Users/ryanyoung/Desktop/Data Science/22575480/data/data/Covid/owid-covid-data.csv")
prior_data<-read.csv("/Users/ryanyoung/Desktop/Data Science/22575480/data/data/Covid/Deaths_by_cause.csv")
combined_data<-bind_rows(covid_data,prior_data)
```

To examine the different Covid experiences by continent, the mean total deaths per million were plotted for each continent. Africa had significantly less cases than the other continents. However, this could be due to low levels of testing
```{r}
#read in data 
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 1/code/new_case_bar.R")
plot_mean_cases_per_million(covid_data)

```

Similarly, Africa has lower total mean deaths per million than other continents. Again this could be related to testing as if people are tested for Covid then their deaths are not reported as Covid deaths.
```{r}
#total deaths per million
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 1/code/total_deaths_bar.R")
chart <- create_mean_deaths_bar_chart(covid_data)
chart


```


This scatter plot shows the relationship between COVID deaths per million and the life expectancy of a country. There is a strong positive correlation between countries with higher life expectancy and COVID deaths suggesting that old people may be more vulnerable.However, life expectancy is correlated to income of a country so we may be underestimating the effect. 
```{r}
#covid deaths by life expectancy 
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 1/code/create_scatter_plot.R")

create_scatter_plot(covid_data)

```

This scatter plot shows the relationship between COVID deaths per million and the percent of a country's population that is over 65. There is a strong positive correlation between those over 65 and COVID deaths suggest old people are more vulnerable.  
```{r}
#covids deaths by percent of population over 65
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 1/code/create_scatter_plot_2.R")

create_scatter_plot_2(covid_data)
```

This chart shows daily hospital and ICU Admissions for 2020 in Asia. Hospital admissions seem to be a leading indicator for ICU admissions. 
```{r}
#hospitals admission chart
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 1/code/patient_admissions_chart.R")
chart <- create_admissions_line_chart(covid_data)
chart

```

