---
title: "Analysis of Metallica and Coldplay"
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5

Ref1: Some Institution, Cape Town, South Africa
Email1: nfkatzke\@gmail.com
Author2: John Smith
Ref2: Some other Institution, Cape Town, South Africa
Email2: John\@gmail.com
CommonAffiliation_12: yes
Author3: John Doe
Email3: Joe\@gmail.com
CorrespAuthor_1: yes
keywords: Multivariate GARCH \sep Kalman Filter \sep Copula
JELCodes: L250 \sep L100
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes

---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)


# Notice that as you are working in a .Rproj file (I am assuming you are) - the relative paths of your directories start at your specified root.
# This means that when working in a .Rproj file, you never need to use getwd() - it is assumed as your base root automatically.


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}


```{r}
#read in the data
coldplay <- read.csv("data/Coldplay_vs_Metallica/Coldplay.csv")
metallica<-read.csv("data/Coldplay_vs_Metallica/metallica.csv")
spotify<-read.csv("data/Coldplay_vs_Metallica/Broader_Spotify_Info.csv")

```

```{r}

#filter songs
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 3/code/filter_songs.R")
metallica_refined <- filter_songs(metallica)
```

The tempo of songs is likely to differ between when it is performed live and when it isn't.A box and whisker plot was used to compare the tempo between live and non-live songs for Metallica.Interesting the tempos have broadly the same mean, with the tempo of live sounds slightly lower.

```{r}
#box and whisker for tempo (live vs non live) metallica
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 3/code/box_whisker_live.R")

plot_live_vs_nonlive_tempo(metallica)
```

The same comparison was also made for Coldplay. Again the mean of the tempo was broadly similar for both live and non-live songs. However, the box for live song's tempo was significantly larger than that of non-live.

```{r}
#box and whisker for tempo (live vs non live) coldplay
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 3/code/box_whisker_live.R")

plot_live_vs_nonlive_tempo(coldplay)
```

The popularity of Metallica's songs over time (release date) was plotted using a line plot. Metallica's initial songs weren't particularly popular;however, after 1990 their population began to pick up. As time went on, their popularity began to wane again. 

```{r}
#Popularity over time metallica
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 3/code/line_plot_ popularity.R")
plot_popularity_over_time(metallica_refined)

```

The popularity of Coldplay's songs was also plotted overtime. Coldplay's every songs were their most popular, followed by songs release between 2010 and 2015. Thereafter, Coldplay's songs have been steadily losing popularity

```{r}
#Popularity over time coldplay
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 3/code/line_plot_ popularity.R")
plot_popularity_over_time(coldplay)
```

Using the Spotify data, the top ten songs by energy were put into a table alongside their artist. One artist, Cattle Decapitation, appear twice in this top ten list.

```{r}
#top songs by energy table
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 3/code/table_energy.R")
top_songs_table <- create_top_songs_table(spotify, 10)
print(top_songs_table)
```

