---
title: "Don't go, London is cold and wet"
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5

Ref1: Some Institution, Cape Town, South Africa
Email1: nfkatzke\@gmail.com
Author2: John Smith
Ref2: Some other Institution, Cape Town, South Africa
Email2: John\@gmail.com
CommonAffiliation_12: yes
Author3: John Doe
Email3: Joe\@gmail.com
CorrespAuthor_1: yes
keywords: Multivariate GARCH \sep Kalman Filter \sep Copula
JELCodes: L250 \sep L100
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes

---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

London, is much colder and wetter than South Africa. 

The graph below shows the daily minimum temperature for London for 2020. The red line shows the average daily minimum temperature in Cape Town (taken from the South African Weather Service). Its clear that London is significantly colder than Cape Town for most of the year. 

```{r}
# load in data:
london_weather <- read_csv("data/london_weather.csv")

```


```{r}
#convert date column
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 2/code/convert_date_column.R")
london_weather <- convert_date_column(london_weather, "date")
```


```{r}
#line chart minimum temp
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 2/code/line_chart_temp.R")
plot_daily_min_temperature(london_weather)
```

Even if you look at the daily mean temperature in London, again compared with Cape Town, you can see the vast majority of the time Cape Town is much warmer.


```{r}
#daily mean temp
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 2/code/plot_daily_temp.R")
plot_mean_temperature(london_weather)
```


The chart here shows the daily precipitation for London in 2020, illustrating that London is wet almost all year round while Cape Town only has a rainy season in the winter but is sunny the rest of the time.

```{r}
#precipitation bar chat
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 2/code/plot_daily_precipitation.R")
b<- plot_daily_precipitation(london_weather)
b
```






