---
title: "New App Information"
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: 
Ref1: Some Institution, Cape Town, South Africa
Email1: nfkatzke\@gmail.com
Author2: John Smith
Ref2: Some other Institution, Cape Town, South Africa
Email2: John\@gmail.com
CommonAffiliation_12: yes
Author3: John Doe
Email3: Joe\@gmail.com
CorrespAuthor_1: yes
keywords: Multivariate GARCH \sep Kalman Filter \sep Copula
JELCodes: L250 \sep L100
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes

---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->




```{r}
#read in the data
googleplay<-read.csv("/Users/ryanyoung/Desktop/Data Science/22575480/data/data/googleplay/googleplaystore.csv")
user_reviews<-read.csv("/Users/ryanyoung/Desktop/Data Science/22575480/data/data/googleplay/googleplaystore_user_reviews.csv")
```

This bubble chart shows the rating of an app versus its size as well as how many installations it has (size of the bubble). Most apps have relatively high ratings and are under 25 MB while installations vary. There any new app made shouldn't be too large if we want good ratings and installations. 

```{r}
#bubble chart (use bubble chart 2)
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 5/code/Bubble_chart_2.R")
chart <- create_bubble_chart(googleplay)
chart
```
 
This table shows app popularity by genre ranked by the average number of downloads. Comics are the most popular genre by download. This is important for developers of new apps to be aware. 
```{r}
#table showing popularity by genre 
source("/Users/ryanyoung/Desktop/Data Science/22575480/Question 5/code/popularity_table.R")
result <- get_average_ratings_downloads(googleplay)
result
```

